MNRAS \LaTeXe\ template -- title goes here

### 2017-06-06 Paper/mnras_template.tex
Some advances

\section{Illustris Simulation}
Illustris-1, also known simply as Illustris, is a highly resolved cosmological simulation which reproduces large-scale statistical features of the Universe, such as the galaxy population of massive clusters, as well as small-scale properties such as the morphology of galaxies and detailed values for their stellar and gas content. This was achieved by following the evolution of $1820^3$ DM particles with mass resolution $m_{\text{DM}} = 6.26\cdot 10^6\text{M}_{\odot}$, together with $1820^3$ baryonic particles with mass resolution $\overline{\text{m}_\text{b}}=1.26\cdot 10^6\text{M}_{\odot}$ from a glass-like configuration, in a periodic box of $106.5\text{Mpc}$, all of which is consistent with a standard $\Lambda \text{CDM}$ cosmology with $\Omega_\Lambda=0.7274$, $\Omega_\text{m}=0.2726$, $\Omega_\text{b}=0.0456$, $\sigma_\text{s}=0.0.809$, $\text{n}_\text{s}=0.963$ \& $\text{H}_0=70.4\text{kms}
^{-1}\text{Mpc}^{-1}$. Illustris has a constant spatial resolution of $1.4\text{kpc}$ for DM particles in comoving units, and for baryonic particles it has the same spatial resolution of DM for $\text{z}\geq 1$, which is later modified to $0.7\text{kpc}$ in physical units for the rest of the simulation. The evolution in time was performed with the hydrodynamic algorithm AREPO \cite{arepo}, which combines a moving Voronoi tessellation with the finite volume approach. Included in the evolution algorithm, there are galaxy formation models which account for the evolution of stars and SMBHs. The level of detail in Illustris is advantageous and hard to find among other simulations, and is the reason why we chose it to perform our calculations.\\

@@

\section{The method}
The principal purpose of this work is to verify if the results obtained observationally by Jones et al. \cite{jones1} are supported by a similar analysis in the cosmological simulation Illustris. For this purpose, we want to adaptate the observational method as closely as posible for it to work on computational data.\\

The principal method used in Jones et al. \cite{jones1} for the analysis of the dependence of the Schechter parameters on the cosmological environment is as follows. To obtain a quantification of environment, they calculated for, each galaxy in the studied survey, the projected distance in the sky to the third nearest neighbor, filtrating candidate galaxies by its radial velocity relative to the galaxy studied. According to Hubble's law, this effectively restricts the candidate galaxies to a smaller radial range, reducing apparent closer galaxies arising from the projection method. The radial relative velocity cut was chosen to be $450km/s$. Furthermore, a photometrics preselection was performed, selecting galaxies whose r-filter magnitude was above $-19$ (VERIFY).\\

Once quantified the environment with the distance to the 3rd nearest neighbor definition for each galaxy in their post-selected survey they divided the group in four quartiles according this quantity. For each quartile, the respective HIMF was calculated, and with this, a Schechter fit was obtained. The analysis was specifically performed over the Schechter parameters of the Knee-mass and the faint-end slope.\\

In dark matter cosmological simulations, acces to the information is istantaneous and at no cost. However, as we want to replicate as closely as possible the method effectuated by Jones et. al \cite{jones1}. We also calculate the projected distance in the simulation, according to a specified point of view, taking the same radial velocity cut having into account distance and peculiar velocities. Even when we could easily calculate the distance to the third nearest neighbor we take into account these observational simplifications, to make our study as comparable as possible to that of Jones et al. \cite{jones1}

>>>>

\section{Illustris Simulation}
Illustris-1, also known simply as Illustris, is a highly resolved cosmological simulation which reproduces large-scale statistical features of the Universe, such as the galaxy population of massive clusters, as well as small-scale properties such as the morphology of galaxies and detailed values for their stellar and gas content. This was achieved by following the evolution of $1820^3$ DM particles with mass resolution $m_{\text{DM}} = 6.26\cdot 10^6\text{M}_{\odot}$, together with $1820^3$ baryonic particles with mass resolution $\overline{\text{m}_\text{b}}=1.26\cdot 10^6\text{M}_{\odot}$ from a glass-like configuration, in a periodic box of $106.5\text{Mpc}$, all of which is consistent with a standard $\Lambda \text{CDM}$ cosmology with $\Omega_\Lambda=0.7274$, $\Omega_\text{m}=0.2726$, $\Omega_\text{b}=0.0456$, $\sigma_\text{s}=0.0809$, $\text{n}_\text{s}=0.963$ \& $\text{H}_0=70.4\text{kms}
^{-1}\text{Mpc}^{-1}$. Illustris has a constant spatial resolution of $1.4\text{kpc}$ for DM particles in comoving units, and for baryonic particles it has the same spatial resolution of DM for $\text{z}\geq 1$, which is later modified to $0.7\text{kpc}$ in physical units for the rest of the simulation. \\

The evolution in time was performed with the hydrodynamic algorithm AREPO \cite{arepo}, which combines a moving Voronoi tessellation with the finite volume approach. Included in the evolution algorithm, there are galaxy formation models which account for the evolution of stars and SMBHs. The level of detail in Illustris is advantageous and hard to find among other simulations, and is the reason why we chose it to perform our calculations.\\

@@

\section{The method}

The principal purpose of this work is to verify if the results obtained observationally by Jones et al. \cite{jones1} are supported by a similar analysis in the cosmological simulation Illustris. For this purpose, we want to adaptate the observational method as closely as posible for it to work on computational data.\\

\subsection{The $3^{rd}$ nearest neighbor method}

The principal method used in Jones et al. \cite{jones1} analyses the dependence of the Schechter parameters on the cosmological environment. To obtain a quantification of said cosmological environment, they calculated for each galaxy in the studied survey the projected distance in the sky to the third nearest neighbor, filtrating candidate neighbors by its radial velocity relative to the reference galaxy. According to Hubble's law, this effectively restricts the candidate galaxies to a smaller radial range, reducing apparent closer galaxies arising from the projection method. The radial relative velocity cut was chosen to be $450km/s$. Furthermore, a photometrics pre-selection was performed, selecting galaxies whose r-filter magnitude was above $-19$ (VERIFY).\\

Once quantified the environment with the distance to the 3rd nearest neighbor definition for each galaxy in their post-selected survey they divided the group in four quartiles according this quantity. For each quartile, the respective HIMF was calculated, and with this, a Schechter fit was obtained. The analysis was specifically performed over the Schechter parameters of the Knee-mass and the faint-end slope. \\

In dark matter cosmological simulations, access to the information is istantaneous and at no cost. However, as we want to replicate as closely as possible the method effectuated by Jones et. al \cite{jones1}, we also calculate the projected distance in the simulation and take the same projected velocity cut according to a specified point of view. Even when we could easily calculate the distance to the third nearest neighbor we take into account these observational simplifications, to make our study as comparable as possible to that of Jones et al. \cite{jones1}.\\

However, as Illustris is a cosmological simulation, it is subject to numerical resolution biases, being the most important, the mass resolution biases. Each mass considered here is subject directly or indirectly to a mass resolution, and the effect it causes is specially evident in the produced mass functions. We used Illustris-3, which is a less resoluted copy of Illustris-1, to verify that the effect on the mass functions is indeed caused by mass resolution. Taking this into account, mass functions are heavily affected for masses below a certain cut and for this reason, only galaxies above said cut are considered in this study. This mass cut has no aparent systematical way to be calculated and therefore, we performed the cut having into account the performance of the respective Schechter fit.\\

Mass resolution reduces the size of the sample galaxies and this complicates the process of photometrics pre-selection. This selection significatively reduces the size of the galaxy set which is already smaller than normal due to the resolution cut. This made impossible a Schechter fit to the obtained mass functions given that the associated logarithmic errors became extremely large. For this reason, we omit the photometrics pre-selection which is the only feature that our analysis misses with respect to the one from \cite{jones1}.\\

\subsection{The cosmic web method}
To complement the analysis performed with the third nearest neighbor method for the classification of environments, we chose a complementary method of completely different nature to verify even more the results from Jones et al.. The method chosen here was
